KidsAIR: manuscript tables/figures

### 2020-06-26 child_health_data_cleaning.Rmd
data cleaning/merging updates

---
title: "Kids health and child data cleaning"
author: "Ethan Walker"
date: "Started 27 Feb 2020, Updated 22 June 2020"
output: pdf_document 
---

@@

# Combine logs from all areas
kids_at_home_log <- rbind(wmt_athomelog_initial, nn_athomelog_initial,
                          ak_athomelog_initial) %>% 
  mutate(area = as.factor(area)) %>% 
  right_join(kids_linked_ids, c("area", "home_winter_id")) %>% 
  filter(!is.na(child_id_num))

@@

# Combine logs from all areas
kids_med_visit <- rbind(wmt_medicalvisit_initial, nn_medicalvisit_initial,
                          ak_medicalvisit_initial) %>% 
  mutate(area = as.factor(area)) %>% 
  right_join(kids_linked_ids, c("area", "home_winter_id"))

@@

# Combine logs from all areas
kids_birth_infancy <- rbind(wmt_birthinfancy_initial, nn_birthinfancy_initial,
                            ak_birthinfancy_initial) %>% 
  mutate(area = as.factor(area)) %>% 
  right_join(kids_linked_ids, c("area", "home_winter_id"))

@@

# Combine logs from all areas
kids_csq <- rbind(wmt_csq_initial, nn_csq_initial, ak_csq_initial) %>% 
  mutate(area = as.factor(area)) %>% 
  right_join(kids_linked_ids, c("area", "home_winter_id")) %>% 
  mutate_if(is.character, as.factor)

>>>>

---
title: "Kids health and child data cleaning"
author: "Ethan Walker"
date: "Started 27 Feb 2020, Updated 26 June 2020"
output: pdf_document 
---

@@

# Combine logs from all areas
kids_at_home_log <- rbind(wmt_athomelog_initial, nn_athomelog_initial,
                          ak_athomelog_initial) %>% 
  mutate(area = as.factor(area)) %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id")) %>% 
  filter(!is.na(child_id_num))

@@

# Combine logs from all areas
kids_med_visit <- rbind(wmt_medicalvisit_initial, nn_medicalvisit_initial,
                          ak_medicalvisit_initial) %>% 
  mutate(area = as.factor(area)) %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id"))

@@

# Combine logs from all areas
kids_birth_infancy <- rbind(wmt_birthinfancy_initial, nn_birthinfancy_initial,
                            ak_birthinfancy_initial) %>% 
  mutate(area = as.factor(area)) %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id"))

@@

# Combine logs from all areas
kids_csq <- rbind(wmt_csq_initial, nn_csq_initial, ak_csq_initial) %>% 
  mutate(area = as.factor(area)) %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id")) %>% 
  mutate_if(is.character, as.factor)

### 2020-06-26 home_char_act_cleaning.Rmd
data cleaning/merging updates

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 22 June 2020"
output: pdf_document
---

@@

# Load, format, and save home char data
```{r}
##### WMT #####
# Load data
home_char_initial_wmt <- read_csv(paste0(file_path, "Input/WMT/homechar.csv"), 
                                  na = c("NULL", ""))

@@

##### NN #####
# Load data
home_char_initial_nn <- read_csv(paste0(file_path, "Input/NN/homechar.csv"), na = c("NULL", ""))

@@

##### AK #####
# Load data
home_char_initial_ak <- read_csv(paste0(file_path, "Input/AK/homechar.csv"), na = c("NULL", ""))

@@

# write_rds(kids_home_char, paste0(file_path, "Output/kids_home_char.rds"))
```

>>>>

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 26 June 2020"
output: pdf_document
---

@@

# Load, format, and save home char data
```{r}
##### WMT #####
# Load data
home_char_initial_wmt <- read_csv(paste0(file_path, "Input/WMT/homechar_updated_data_SAVE.csv"), 
                                  na = c("NULL", ""))

@@

##### NN #####
# Load data
home_char_initial_nn <- read_csv(paste0(file_path, "Input/NN/homechar_updated_data_SAVE.csv"), na = c("NULL", ""))

@@

##### AK #####
# Load data
home_char_initial_ak <- read_csv(paste0(file_path, "Input/AK/homechar_updated_data_SAVE.csv"), na = c("NULL", ""))

@@

write_rds(kids_home_char, paste0(file_path, "Output/kids_home_char.rds"))
```

### 2020-06-26 home_char_act_summary.Rmd
data cleaning/merging updates

>>>>

# Check Winter 1 vs Winter 2 data for home characteristics
```{r}
home_char_check_num <- home_char_clean %>% 
  group_by(home) %>% 
  arrange(home, winter_id) %>% 
  pivot_longer(cols = c(residents_total:residents_under18, home_year_built:home_furry), 
               names_to = "var", values_to = "value") %>% 
  group_by(home, var) %>% 
  arrange(home, var, winter_id) %>% 
  mutate(data_check = if_else(value == lead(value), 1, 0),
         data_check = if_else(is.na(data_check), lag(data_check), data_check)) %>% 
  filter(data_check == 0) %>% 
  select(area, home, home_winter_id, winter_id, var, value) %>% 
  mutate(value = as.numeric(value),
         data_check = if_else(var == "residents_total" & abs(value - lead(value)) > 1, 1, 0),
         data_check = if_else(var == "residents_under5" & abs(value - lead(value)) > 1, 1, data_check),
         data_check = if_else(var == "residents_under18" & abs(value - lead(value)) > 1, 1, data_check),
         data_check = if_else(var == "home_year_built" & abs(value - lead(value)) > 10, 1, data_check),
         data_check = if_else(var == "home_sqft" & abs(value - lead(value)) > 200, 1, data_check),
         data_check = if_else(var == "home_floors" & abs(value - lead(value)) > 1, 1, data_check),
         data_check = if_else(var == "home_bedrooms" & abs(value - lead(value)) > 1, 1, data_check),
         data_check = if_else(var == "home_windows" & abs(value - lead(value)) > 5, 1, data_check),
         data_check = if_else(var == "home_pets" & abs(value - lead(value)) > 2, 1, data_check),
         data_check = if_else(var == "home_furry" & abs(value - lead(value)) > 2, 1, data_check),
         data_check = if_else(is.na(data_check), lag(data_check), data_check),
         value = as.character(value)) %>% 
  filter(data_check == 1) %>% 
  select(area, home, home_winter_id, winter_id, var, value)

write_csv(home_char_check_num, paste0(file_path, "Output/home_char_check_num.csv"))

home_char_check_fact <- home_char_clean %>% 
  group_by(home) %>% 
  arrange(home, winter_id) %>% 
  pivot_longer(cols = c(home_type, stove_age, stove_cert, home_fireplace:home_insert), 
               names_to = "var", values_to = "value") %>% 
  group_by(home, var) %>% 
  arrange(home, var, winter_id) %>% 
  mutate(data_check = if_else(value == lead(value), 1, 0),
         data_check = if_else(is.na(data_check), lag(data_check), data_check)) %>% 
  filter(data_check == 0) %>% 
  select(area, home, home_winter_id, winter_id, var, value) %>% 
  mutate(var2 = var,
         value2 = value) %>% 
  pivot_wider(names_from = "var2", values_from = "value2") %>% 
  ungroup() %>% 
  mutate_at(c("home_insert", "stove_age", "home_furnace", "home_woodstove", 
              "stove_cert", "home_type", "home_fireplace"), as.character) %>% 
  mutate_at(c("home_insert", "stove_age", "home_furnace", "home_woodstove", 
              "stove_cert", "home_type", "home_fireplace"), as.factor) %>% 
  mutate_at(c("home_insert", "stove_age", "home_furnace", "home_woodstove", 
              "stove_cert", "home_type", "home_fireplace"), as.numeric)

home_char_check_fact$value_num <- 
  coalesce(home_char_check_fact$home_insert, 
           home_char_check_fact$stove_age, 
           home_char_check_fact$home_furnace, 
           home_char_check_fact$home_woodstove, 
           home_char_check_fact$stove_cert, 
           home_char_check_fact$home_type, 
           home_char_check_fact$home_fireplace)

home_char_check_fact2 <- home_char_check_fact %>% 
  select(area, home,home_winter_id, winter_id, var, value, value_num) %>% 
  group_by(home, var) %>% 
  mutate(data_check = if_else(abs(value_num - lead(value_num)) > 1, 1, 0),
         data_check = if_else(is.na(data_check), lag(data_check), data_check),
         value = as.character(value))

write_csv(home_char_check_fact2, paste0(file_path, "Output/home_char_check_fact.csv"))

home_char_check <- rbind(home_char_check_num, home_char_check_fact2) %>% 
  arrange(home, var, winter_id) %>% 
  mutate(data_check = if_else(is.na(value_num), 1, data_check))

write_csv(home_char_check, paste0(file_path, "Output/home_char_check.csv"))
```

### 2020-06-26 manuscript_tables_figures.Rmd
data cleaning/merging updates

---
title: 'KidsAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 13 May 2020, Updated 22 May 2020"
output:
  powerpoint_presentation: default
---

@@

@@

```{r}
# number of placebo households, total and by area
placebo_homes <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1) %>% 
  filter(area == "WMT") %>% 
  select(area, home, home_id, winter_id, home_winter_id, treatment)
  #filter(treatment == "Placebo") %>% 
  distinct(home, .keep_all = TRUE) %>%
  count(area)
placebo_homes

# number of placebo households, total and by area
treatment_homes <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 2) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  group_by(area) %>% 
  count(treatment)
treatment_homes

# number of placebo households, total and by area
treatment_kids <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 2) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  filter(!is.na(child_id_num)) %>% 
  group_by(area) %>% 
  count(treatment)
treatment_kids
```

>>>>

---
title: 'KidsAIR: manuscript tables/figures'
author: "Ethan Walker"
date: "Started 13 May 2020, Updated 26 June 2020"
output:
  powerpoint_presentation: default
---

@@

health_data_merged <- 
  read_rds(paste0(file_path, "Output/health_data_merged.rds"))

@@

```{r}
# number of households, total and by area
study_homes <- health_exposure_data_sampling_day %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>%
  count(area, winter_id, treatment_assigned)
study_homes

study_kids <- health_exposure_data_sampling_day %>% 
  filter(!is.na(child_id_num)) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>%
  count(area, winter_id, treatment_assigned)
study_kids

nn_homes <- health_exposure_data_sampling_day %>% 
  filter(home == "CH209" | home == "CH218")
```
